Workflow

### 2014-08-02 Workflow/Workflow.Rmd
Minor changes.

This makes the historical data available to the nodes of dahl.
This command doesn't work from fs1 or any of the other nodes of dahl (node-01 through node-42).

@@

### Submit the job to dahl
* `cd` to the `Econ-Growth-R-Analysis` directory from fs1.calvin.edu.
* Run `Scripts/<Source>_batch.bash "-n 2 -C -d"` followed by `more data_resample/<SOURCE>/node*.txt` to obtain a printout of what will be executed.    
* Run `Scripts/<Source>_batch.bash "-n 2 -C"` to test that things work as expected.
* Then do `Scripts/<Source>_batch.bash "-n 1000 -C"` to do a complete run.
* Check dahl's status at (http://fs1.calvin.edu/ganglia/?m=load_one&r=hour&s=by%2520name&c=dahl&h=&sh=1&hc=4&z=small).
* Check progress with `more data_resample/<Source>/node-*.txt`.

@@

### Download post-processed results to local machine
* From a local computer, say `Scripts/DownloadResults.R -u <user> -S <Source> -d`, where `<user>` is 
a username on dahl, `<Source>` is the data source of interest, and `-d` will 
print the files to be transferred to the local machine, rather than transfer them.
* Verify that the list of files to be transferred looks right.
* From a local computer, say `Scripts/DownloadResults.R -u <user> -S <Source>` to download the files.
* The files are downloaded to the `Packages/EconData/tmp_big_data` directory on the local machine.
* Manually move the files to `Packages/EconData/data` if you want them to be available in the `EconData` package.
This manual step avoids large data files automatically included in the `EconData` package, 
thereby slowing everything down.

>>>>

This makes the historical data available to the nodes of dahl.
This command doesn't work from `fs1` or any of the other nodes of dahl (node-01 through node-42).

@@

### Submit the job to dahl
* `cd` to the `Econ-Growth-R-Analysis` directory from `fs1.calvin.edu`.
* Run `Scripts/<Source>_batch.bash "-n 2 -C -d"` followed by `more data_resample/<SOURCE>/node*.txt` to obtain a printout of what will be executed.    
* Run `Scripts/<Source>_batch.bash "-n 2 -C"` to test that things work as expected.
* Then do `Scripts/<Source>_batch.bash "-n 1000 -C"` to do a complete run.
* Check dahl's status at (http://fs1.calvin.edu/ganglia/?m=load_one&r=hour&s=by%2520name&c=dahl&h=&sh=1&hc=4&z=small).
* Check progress with `more data_resample/<Source>/node-*.txt`.

@@

### Download post-processed results to local machine
* From a local computer, say `Scripts/DownloadResults.R -u <user> -S <Source> -d`, where `<user>` is 
a username on dahl, `<Source>` is the data source of interest, and `-d` will 
print the files to be transferred to the local machine, rather than transfer them.
* Verify that the list of files to be transferred looks right.
* From a local computer, say `Scripts/DownloadResults.R -u <user> -S <Source>` to download the files.
* The files are downloaded to the `Packages/EconData/tmp_big_data` directory on the local machine.
* Manually move the files to `Packages/EconData/data` if you want them to be available in the `EconData` package.
This manual step prevents large data files from being automatically included in the `EconData` package, 
thereby slowing everything down.
